\textbf{Name:} \\

\medskip

\textbf{Conspirators:} 

\medskip
\medskip

\hrule

\medskip


\assignmentsonly{\pleasesubmitprojectdraft}

Finish your projects:
\begin{itemize}
\item
  Final report page minima:
  \begin{itemize}
  \item[]
    $\sim$ 3 pages for groups of 1.
  \item[]
    $\sim$ 4 pages for groups of 2.
  \item[]
    $\sim$ 5 pages for groups of 3.
  \item[]
    $\sim$ 6 pages for groups of 4.
  \end{itemize}
\item
  Final talk, 3:00 per person.
\end{itemize}

Instructions:

\begin{itemize}
\item 
  Final presentations and project write-ups are due by Friday, 11:59 pm, December 16
  (the day of the course's final exam period).
\item 
  Please submit recorded videos and pdfs via Blackboard.
\item
  We will organize for the videos to be uploaded to the course's Teams site.
\end{itemize}


Here's what you need to know and do. Grading will take into account all of these aspects and more.

\begin{enumerate}
\item 
  Talks should absolutely be G rated and respectful of others.
  See the PoCS
  \wordwikilink{\coursewebsite/docs/2022-2023pocsverse-syllabus.pdf}{syllabus},
  UVM's student conduct standards, and UVM's
  \wordwikilink{https://www.uvm.edu/president/our-common-ground}{Our Common Ground}.

\item
  Time: Please aim for no more than 3 minutes per person.

\item
  Your mission is to:
  \begin{enumerate}
  \item
    quickly review the problem/area you've been investigating; and
  \item
    describe what you've been able to achieve so far (or what went horribly wrong).
  \end{enumerate}

  Please re-introduce yourself in a sentence (name + your field),
  and to acknowledge who you're working with.

\item
  Talks will be made available on Microsoft Streams for viewing on the day of the final exam.

\item
  Slides: Suggest 3 to 5.  More may work but
  \wordwikilink{https://www.youtube.com/watch?v=xOrgLj9lOwk}{100 is right out}. Quality of slides forms part of the grade.

\item
  If you are feeling up for Beamer/LaTeX, I highly encourage it. Keynote is fine as well. Anything that ends up as a pdf will work.

\item
  Here's the Deliverator's universal paper template that will work on Overleaf:
  \wordwikilink{https://github.com/petersheridandodds/universal-paper-template}{https://github.com/petersheridandodds/universal-paper-template}.

  This is the PoCS-preferred paper production system.
\item
  Overleaf also provides many journal format templates. The universal template builds out from Physical Review's template:
  \wordwikilink{https://www.overleaf.com/latex/templates/revtex-4-dot-2-template-and-sample/yydsrzvrqrzs}{https://www.overleaf.com/latex/templates/revtex-4-dot-2-template-and-sample/yydsrzvrqrzs}.

\item
  Practice!  These are short talks so you can run through
  them a number of times to straighten everything out.


\end{enumerate}

